Full Title

### 2019-10-06 draft/paper.tex
misc

%% Journal information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{ICFP} % CONF = POPL or ICFP or OOPSLA
\acmArticle{1}
\acmYear{2018}
\acmMonth{1}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

@@

%% Title information
\title[Short Title]{Staged Abstract Interpreter}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
\subtitle{Subtitle}                     %% \subtitle is optional
\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  We present Staged Abstract Interpreter
\end{abstract}

@@

%% Keywords
%% comma separated list
\keywords{generic programming, abstract interpretation, static analysis}  %% \keywords are mandatory in final camera-ready submission

@@

\textbf{Outline(Proposed)}.

1. Revisit abstract compilation (generates textual program and closures)

2. Generalize the idea to staged abstract interpreter.
We implement staged abstract interpreter within a big-step abstract semantics 
(abstract definitional interpreter) using Scala with LMS framework.  
Show that abstract compilation can be understood as an instance of staged 
abstract interpreter.

Extension: can we do it with small-step semantics? or staging a transition system?

3. Improve performance (closure is still not an efficient enough representation).

Show it generates sound and high-performance low-level analysis code with 
various precisions and sensitivities, for instances, k-CFA, pushdown or m-CFA.

Store/set operations (join, update) is also expensive, generating efficient store implementation\cite{liang2014fast}.

4. Modular analysis for free?

Motivation: one of the challenges of modern static analysis is program usually depends on
large libraries programs\cite{toman_et_al:LIPIcs:2017:7121}. 
Can we analyze programs and libraries separately without losing precision? So that we can 
reduce part of the overhead of repeatedly analyzing libraries for different programs.
Similarly, some static analyzers compute summary for a function or a module, that can be reused
later (like Facebook Infer). But to my knowledge, they are mostly context-insensitive or imprecise.

Application: for example, k-CFA (k > 0) is naturally a kind of whole program analysis, because 
it need the last k calling contexts as abstraction. But can we analyze programs (libraries) separately 
which generate the specialized analysis and leave the k calling contexts as dynamic parameters, 
and then install these contexts when we have the whole program.

Another perspective: programs are data for an abstract interpreter, so if we have $n$ programs, 
then there can be $n$ stages. 
Probably we can analyze first $m$ programs, and generate a residual abstract interpreter
waiting for the rest $(n-m)$ programs.

Not sure how much improvement of performance.

5. Show the evaluation result on benchmark programs (TODO: collect benchmark programs). 
Compare with normal abstract interpreter, 
abstract compilation\cite{Boucher:1996:ACN:647473.727587}, and OAAM \cite{Johnson:2013:OAA:2500365.2500604}.

\section{Background}

\subsection{Abstracting Abstract Machine}

\subsection{Staged Interpreter}

\section{Abstract Compilation, Revisited}

\section{Staged Abstract Interpreter}

\section{Evaluation}

@@

\textbf{Abstract Compilation}. The idea in this paper is closely inspired by 
abstract compilation \cite{Boucher:1996:ACN:647473.727587}.
\citeauthor{Boucher:1996:ACN:647473.727587} presented abstract compilation
techniques as an efficient implementation of the monovariant flow analysis 
\textit{0}-CFA for programs in continuation-passing style. The key idea is to 
reduce the interpretation overhead on traversing the syntax tree by partial evaluation.
Specifically, they proposed two kinds of abstract compilers to achieve this. 
The first one is to generate specialized analysis as a textual program, then 
can be loaded and executed by \texttt{eval} or similar mechanisms. The second 
one is using closure as a representation of specialized analysis. 
A closure is a function that remembers the environment where it defined. So the 
abstract compiler generates higer-order functions on-the-fly rather than textual 
program, then the functions can be applied immediately in a higher-order host language.

\citeauthor{Johnson:2013:OAA:2500365.2500604} in their work also adopt the 
idea closure generation for optimizing small-step abstracting abstract machine
\cite{Johnson:2013:OAA:2500365.2500604}. The source program is firstly compiled
to intermediate form called "abstract bytecode", which are actually higher-order functions, 
and then executed on a abstract abstract machine.

\citeauthor{damian1999partial}'s work on partial evaluation for program analysis \cite{damian1999partial}.

\citeauthor{amtoft1999partial}'s work on partial evaluation for constraint-based 
control flow analysis \cite{amtoft1999partial}.

\textbf{Abstracting Abstract Machine}. Abstracting Definitional Interpreter \cite{darais2017abstracting}

Collapsing Towers of Interpreters\cite{Amin:2017:CTI:3177123.3158140}

\section{Conclusion}

@@

%% Bibliography
\bibliography{references}

>>>>

%% Journal information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{CONF} % CONF = POPL or ICFP or OOPSLA
\acmArticle{1}
\acmYear{2018}
\acmMonth{1}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

@@

%% Title information
\title[Short Title]{Full Title}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
\subtitle{Subtitle}                     %% \subtitle is optional
\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
Text of abstract \ldots.
\end{abstract}

@@

%% Keywords
%% comma separated list
\keywords{keyword1, keyword2, keyword3}  %% \keywords are mandatory in final camera-ready submission

@@

Text of paper \ldots

\cite{Futamura1999, Futamura1971}

@@

Along with dynamic taint analysis, forward symbolic execution is widely used in
software security and bug finding. \citet{DBLP:conf/sp/SchwartzAB10} discussed
those techniques in a security context. Using a simple low-level intermediate
language, they presented a formalization of forward symbolic execution in the form of
small-step operational semantics. Existing challenges of symbolic execution and
potential mitigations are also discussed.

\cite{Siddiqui:2012:SSE:2245276.2231988}

@@

%% Bibliography
\bibliography{references,symexe}
